Redundant calibration as a complex optimization problem

### 2016-12-14 paper.tex
added prec error plot
started red calibration section properly

\section{Redundant Calibration}

@@

>>>>

\section{Redundant Calibration}
Redundant calibration can be formulated as a least-squares problem:
\begin{equation}
\label{eq:least_squares_red}
\min_{\bz} \|\br\| = \min_{\bz} \|\bd - \bv(\bz)\|, 
\end{equation}
where $\bz = [\bg^T,\by^T]^T$. As discussed in Section~\ref{}, we can solve the above minimization problem in one of two ways. We can split the problem into its real and
imaginary parts and then solve for the real and imaginary parts of the parameters seperately or we can employ the notion of Wirtinger derivatives. The former 
approach is discussed in detail in Section~\ref{}, while the latter approach is described in Section~\ref{}.

@@

\begin{figure}
\includegraphics[width=0.47\textwidth]{./prec_error.pdf} 
\caption{Precentage Error}
\label{fig:prec_error}
\end{figure}
